DP Problems of Interest

### 2012-10-01 docs/roadmap/problems.tex
Nussinov.

\item Recurrence:
\[\begin{array}{rcl}
W_{(i,j)}&=&\min\left\{\begin{array}{l|l}
	W_{(i+1,j)}+b & S\\
	W_{(i,j-1)}+b & W\\
	V_{(i,j)}+\delta(S_i,S_j) & ?V? \\
	\min_{i<k<j}W_{(i,k)}+W_{(k+1,j)} & ?k?
\end{array}\right.\\
\\
V_{(i,j)}&=&\min\left\{\begin{array}{ll}
	\infty \qquad\qquad\qquad\qquad {\rm if}(S_i,S_j) \text{ is not a base pair}\\
	eh(i,j)+b \qquad\qquad\, \text{otherwise} \\
	V_{(i+1,j-1)}+es(i,j) \\
	VBI(i,j) \\
	\min_{i<k<j-1}\{W_{(i+,k)}+W_{(k+1,j-1)}\} +c
\end{array}\right.\\
\\
 F_{(j)}&=&\min\left\{\begin{array}{ll} F_{(j-1)} \\ \min_{1\le i< j} (V_{(i,j)} + F_{(j-1)})
%
\end{array}\right. \text{(Free Energy)}\\\\
VBI(i,j)&=&\min_{i<i'<j'<j}\{V_{(i',j')}+ebi(i,j,i',j')\} +c
\end{array}\]

\item Backtracking: XXX
\item Visualisation: XXX
\item Optimizations: XXX
}
\ole

% ------------------------------------------------------------------------------------------------
\newpage
\section{Plan} \ol
\item Define/agree the maoin problems/classes to take into consideration: dimension, serial/non-serial, monadic/polyadic, ... add some other problems that belong to this class or simpler classes
\item Concerns separation: common architecture enables flexibility (exchange components) \ul
	\item Block processor: CPU, GPU, FPGA, must allow variation of width and height
	\item Memory stats computation (min, sum, ... column/line combinations): CPU, GPU
	\item Scheduler (CPU): interleave block computation and memory statistics
	\ule
\item Common description \ul
	\item Block kernel processor
	\item Full block
	\ule
\item Discussion: wavefront, design similarities, polyhedral theory
\ole

>>>>

\item Recurrence:
\[\begin{array}{rcl}
W_{(i,j)}&=&\min\left\{\begin{array}{l|l}
	W_{(i+1,j)}+b & S\\
	W_{(i,j-1)}+b & W\\
	V_{(i,j)}+\delta(S_i,S_j) & ?V? \\
	\min_{i<k<j}W_{(i,k)}+W_{(k+1,j)} & ?k?
\end{array}\right.\\
\\
V_{(i,j)}&=&\min\left\{\begin{array}{ll}
	\infty \qquad\qquad\qquad\qquad {\rm if}(S_i,S_j) \text{ is not a base pair}\\
	eh(i,j)+b \qquad\qquad\, \text{otherwise} \\
	V_{(i+1,j-1)}+es(i,j) \\
	VBI(i,j) \\
	\min_{i<k<j-1}\{W_{(i+,k)}+W_{(k+1,j-1)}\} +c
\end{array}\right.\\
\\
 F_{(j)}&=&\min\left\{\begin{array}{ll} F_{(j-1)} \\ \min_{1\le i< j} (V_{(i,j)} + F_{(j-1)})
%
\end{array}\right. \text{(Free Energy)}\\\\
VBI(i,j)&=&\min_{i<i'<j'<j}\{V_{(i',j')}+ebi(i,j,i',j')\} +c
\end{array}\]
\item Backtracking: XXX
\item Visualisation: XXX
\item Optimizations: XXX
}
\ole

% ------------------------------------------------------------------------------------------------
\newpage
\section{Plan} \ol
\item Make sure we encompass all the most common patterns of DP: check if we have higher dimensions or more complex formula.
\item Let the user tune the window size if he wants to reduce non-serial to serial.

\item Concerns separation: common architecture enables flexibility (exchange components) \ul
	\item Block processor: CPU, GPU, FPGA, must allow variation of width and height
	\item Memory stats computation (min, sum, ... column/line combinations): CPU, GPU
	\item Scheduler (CPU): interleave block computation and memory statistics
	\ule
\item Common description \ul
	\item Block kernel processor
	\item Full block
	\ule
\item Discussion: wavefront, design similarities, polyhedral theory
\ole
